{{ cookiecutter.paper_title}}

### 2018-08-24 {{ cookiecutter.repo_name }}/Paper/paper.tex
Annoying curly brackets
Trying to fix issue

%% Author
\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{
    % Author List
    {{ cookiecutter.author_first_name + '_' + cookiecutter.author_last_name }}$^{1}$\thanks{Email: \mailto{ {{cookiecutter.author_email}} }}\\
    $^{1}$ {{ cookiecutter.author_affiliation}}
}

@@

%% Publication year
%% -- Enter the current year, for the copyright statements, etc.
\pubyear{{{ cookiecutter.paper_pubyear}}}

@@

\bibliographystyle{mnras}
\bibliography{Mendeley}

>>>>

%% Author
\author[{{ cookiecutter.author_last_name + 'et al. ' + cookiecutter.paper_pubyear}}]{
    % Author List
    {{ cookiecutter.author_name }}$^{1}$\thanks{Email: \mailto{{{ cookiecutter.author_email }}}}\\
    $^{1}$ {{ cookiecutter.author_affiliation}}
}

@@

%% Publication year
%% -- Enter the current year, for the copyright statements, etc.
\pubyear{ {{ cookiecutter.paper_pubyear}} }

@@

\bibliographystyle{mnras}
\bibliography{Mendeley.bib}
